Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-09 draft.tex
Put authors into a separate file

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$,
  \textbf{Konrad Hinsen}$^{4,5}$,
  \textbf{Thomas Arildsen}$^{?}$,
  \textbf{Lorena Barba}$^{?}$,
  \textbf{Fabien Benureau}$^{?}$,
  \textbf{C. Titus Brown}$^{?}$,
  \textbf{Georgios Detorakis}$^{?}$,
  \textbf{Emmanuelle Gouillart}$^{?}$,
  \textbf{Pierre de Buyl}$^{?}$,
  \textbf{Benoît Girard}$^{?}$,
  \textbf{Olivia Guest}$^{?}$,
  \textbf{Mehdi Khamassi}$^{?}$,
  \textbf{Etienne Roesch}$^{?}$,
  \textbf{Joseph Stachelek}$^{?}$,
  \textbf{Owen Petchey}$^{?}$,
  \textbf{Timothée Poisot}$^{?}$,
  \textbf{Karthik Ram}$^{?}$,
  \textbf{Yoav Ram}$^{?}$
  \textbf{Federico Vaggi}$^{?}$,
  \textbf{Julien Vitay}$^{?}$,
  \textbf{Tiziano Zito}$^{?}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France
    $^{2}$Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS, UMR 5293, Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, Talence, France
    $^{4}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans Cedex 2
    $^{5}$Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

>>>>

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
    \input{authors.tex}
  \end{small}
\begin{footnotesize}
  \vspace{2mm}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France --
          Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS UMR 5293, Bordeaux, France -- 
          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS UMR 5800, Talence, France •
    $^{2}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans --
          Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}
